\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

Systematic uncertainties in high energy physics, representing our incomplete
knowledge in the simulation of physical processes or in the detection apparatus,
may cause variations in the conditional distributions of features used for
training a classifier.  As such, the efficacy of a classifier may change under
the variations caused by systematic uncertainties.  In this paper, we repurpose
adversarial training as a means to produce a pivotal classifier which is
invariant to variations of the nuisance parameters which parameterize the
effects of systematic uncertainties. In the machine learning context, this
problem is closely related to those of domain adaptation and enforcing fairness
in classification. Following that line of work, the method proposed in this work
can be regarded as generalization that also supports the continuous case,
which can be viewed as handling infinitely many domains or as enforcing fairness
over continuous attributes.

@@

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.48\textwidth]{figures/f-plain.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-plain.pdf}\\
        \vspace{-0.8cm}
        \includegraphics[width=0.48\textwidth]{figures/f-adversary.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-adversary.pdf}
    \end{center}
    \vspace{-1cm}
    \caption{Toy example.
    (Upper left) Conditional probability densities of the decision scores for $Z=0, 1, 2$
       when $f$ is built without adversarial training. The resulting densities
       are clearly dependent on $Z$, indicating that $f$ is not pivotal.
    (Upper right) The corresponding decision surface, highlighting
       the fact that samples are easier to classify for values of $Z$ closer to $2$,
       hence partially explaining the dependency.
    (Lower left) Conditional probability densities of the decision scores for $Z=0, 1, 2$ when $f$ is
       built with adversarial training, as outlined in Section~\ref{sec:method}.
       The resulting densities are now almost identical to each other, indicating only a
       small dependency on $Z$.
    (Lower right) The corresponding decision surface, illustrating how adversarial
       training bends the decision function vertically to erase the dependency on $Z$.
    }
    \label{fig:toy}
\end{figure*}

>>>>

Systematic uncertainties in high energy physics, representing our incomplete
knowledge in the simulation of physical processes or in the detection apparatus,
may cause variations in the conditional distributions of features used for
training a classifier.  As such, the efficacy of a classifier may change under
the variations caused by systematic uncertainties.  In this paper, we repurpose
adversarial training as a means to produce a pivotal classifier which is
invariant to variations of the nuisance parameters describing the
effects of systematic uncertainties. In the machine learning context, this
problem is closely related to those of domain adaptation and enforcing fairness
in classification. Following that line of work, the method proposed in this work
can be regarded as generalization that also supports the continuous case,
which can be viewed as handling infinitely many domains or as enforcing fairness
over continuous attributes.

@@

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.48\textwidth]{figures/f-plain.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-plain.pdf}\\
        \vspace{-0.8cm}
        \includegraphics[width=0.48\textwidth]{figures/f-adversary.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-adversary.pdf}
    \end{center}
    \vspace{-1cm}
    \caption{Toy example.
    (Upper left) Conditional probability densities of the decision scores at $Z=0, 1, 2$
       when $f$ is built without adversarial training. The resulting densities
       are clearly dependent on the continuous parameter $Z$, indicating that $f$ is not pivotal.
    (Upper right) The corresponding decision surface, highlighting
       the fact that samples are easier to classify for values of $Z$ closer to $2$,
       hence partially explaining the dependency.
    (Lower left) Conditional probability densities of the decision scores at $Z=0, 1, 2$ when $f$ is
       built with adversarial training, as outlined in Section~\ref{sec:method}.
       The resulting densities are now almost identical to each other, indicating only a
       small dependency on $Z$.
    (Lower right) The corresponding decision surface, illustrating how adversarial
       training bends the decision function vertically to erase the dependency on $Z$.
    }
    \label{fig:toy}
\end{figure*}
